---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# xplorerr

[![CRAN_Status_Badge](http://www.r-pkg.org/badges/version/xplorerr)](https://cran.r-project.org/package=xplorerr)
[![Travis-CI Build Status](https://travis-ci.org/rsquaredacademy/xplorerr.svg?branch=master)](https://travis-ci.org/rsquaredacademy/xplorerr)
[![AppVeyor Build Status](https://ci.appveyor.com/api/projects/status/github/rsquaredacademy/xplorerr?branch=master&svg=true)](https://ci.appveyor.com/project/rsquaredacademy/xplorerr)
[![](https://cranlogs.r-pkg.org/badges/grand-total/xplorerr)](https://cran.r-project.org/package=xplorerr)

## Overview

xplorerr provides a set of shiny apps useful for:

- generating descriptive & summary statistics
- exploring statistical distributions
- hypothesis testing
- data visualization
- and modeling

## Installation

You can install xplorerr from github with:

```{r gh-installation, eval = FALSE}
# install xplorerr from CRAN
install.packages('xplorerr')

# install.packages("devtools")
devtools::install_github("rsquaredacademy/xplorerr")
```

## Usage

There are five apps in xplorerr which can be launched using `launch_app_*` prefix (easy tab completion)

### Descriptive Statistics

```{r descriptr, eval=FALSE}
launch_app_descriptr()
```

### Hypothesis Testing

```{r inferr, eval=FALSE}
launch_app_inferr()
```

### Visualization

```{r visualize, eval=FALSE}
launch_app_visualizer()
```

### Model Building

```{r olsrr, eval=FALSE}
launch_app_olsrr()
```

### Xplorerr

```{r xplorerr, eval=FALSE}
launch_app_xplorerr()
```


Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
